Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-05-09 research_proposal/research_proposal_draft.qmd
writing sim section and put table

The experimental design is to simulate a hierarchical time series data set, then apply the MinT reconciliation method with different covariance estimators. The data set will be split into training and test sets. In case of cross-validation, the training set will be further split into training and validation sets. The data generating process is described in @sec-dgp Appendix.

>>>>

The experiment starts from simulating a hierarchical time series data set, then applying the MinT reconciliation method with different covariance estimators. The data set will be split into training and test sets. In the case of performing NOVELIST cross-validation, the training set will be further split into training and validation sets equally.

In this preliminary experiment, we consider a slightly large hierarchical structure. The structure consists of 3 levels with a total of 45 series. The bottom level has 36 series and are aggregated in groups of size six to form six level-1 series. The level-1 series are then aggregated in groups of size three to form two level-2 series, which are finally aggregated to form the top level. The observations at bottom level is generated from a VAR(1) process. A more detailed data generating process is described in @sec-dgp Appendix.

For each series, $T = 116$ or $316$ observations are generated. The first 100 or 300 observations are used for training, and the last 16 observations are used for testing. The remaining data is used to compute the best fitted ARIMA models by minimising the AICc criterion. We refer to them as base models, and their base forecasts are then reconciled using the MinT with different covariance estimators. These include using the unbiased sample covariance matrix - MinT(Sample), the shrinkage estimator - MinT(Shrink), and the NOVELIST estimator - MinT(N). The Monte Carlo simulation is repeated 500 times, in which the parameters for data generating process is also randomly generated. The results are presented in @tbl-sim-summary.

```{r tbl-sim-summary}
#| echo: false
#| message: false
#| warning: false

# Code --------------------------------------
library(tidyr)
library(ggplot2)
library(tsibble)
library(dplyr)
library(purrr)
library(kableExtra)
library(knitr)

sim1 <- readRDS("D:/Github/Recon_Honours_Thesis/research_proposal/sim_results/S36-6-2-1_T100_M500_par.rds")
sim2 <- readRDS("D:/Github/Recon_Honours_Thesis/research_proposal/sim_results/S36-6-2-1_T300_M500_par.rds")

transfrom_sim_MSE <- function(MSE, to_ts = T) {
  df <- imap_dfr(MSE, function(mat, model_name) {
    as_tibble(mat) %>%
      mutate(h = row_number()) %>%
      pivot_longer(cols = -h, names_to = "series", values_to = "MSE") %>%
      mutate(
        .model = model_name,
      ) %>%
      select(.model, series, h, MSE)
  })
  if (to_ts) {
    return(
      as_tsibble(key = c(.model, series), index = h)
    )
  }
  return(df)
}

MSE1 <- transfrom_sim_MSE(sim1$MSE, F)
MSE2 <- transfrom_sim_MSE(sim2$MSE, F)

hier_level <- MSE1$series |>
  substring(1, 1) |>
  unique() |> sort(decreasing = TRUE)

MSE_full <- bind_rows(MSE1, MSE2, .id = "id") |>
  mutate(
    level = match(substring(series,1,1), hier_level)
  )

group_defs <- tibble(
  h_group = c("h=1",  "h=1-8",   "h=1-16"),
  h_max   = c(1,      8,         16)
)

MSE_tidy <- MSE_full %>%
  # filter(h<=16) %>%
  crossing(group_defs) %>%    # gives every row all 3 candidate groups
  filter(h <= h_max) %>%      # keep only the overlapping ones
  # filter(h>15)
  group_by(id, .model, level, h_group) %>%
  summarise(mean_MSE = mean(MSE), .groups = "drop")

MSE_tidy <- MSE_tidy %>%
  group_by(level, id, h_group) %>%
  mutate(
    base_MSE = mean_MSE[.model == "base"],
    change = if_else(.model == "base",
                     formatC(mean_MSE, digits = 1, format = "f"),
                     formatC(100 * (mean_MSE - base_MSE) / base_MSE, digits = 1, format = "f"))
  ) %>%
  ungroup()

MSE_tidy <- MSE_tidy %>%
  pivot_wider(
    id_cols = c(level, .model),
    names_from = c(id, h_group),
    values_from = change
  ) %>%
  mutate(
    .model = recode(.model,
                    "mint_sample" = "MinT(Sample)",
                    "mint_shr"    = "MinT(Shrink)",
                    "mint_n"      = "MinT(N)",
                    "base"        = "Base"
    ),
    .model = factor(.model, levels = c("MinT(Sample)", "MinT(Shrink)", "MinT(N)", "Base"))
  ) %>%
  mutate(
    level = recode(level,
                   `1` = "Top level",
                   `2` = "Level 1",
                   `3` = "Level 2",
                   `4` = "Bottom level"
    ),
    level = factor(level, levels = c("Top level", "Level 1", "Level 2", "Bottom level"))
  ) %>%
  arrange(level, .model)

row_levels <- MSE_tidy$level
MSE_display <- MSE_tidy %>% select(-level)

# Kable --------------------------------------
my_kable <- MSE_display %>%
  mutate(across(where(is.numeric), ~formatC(.x, digits = 1, format = "f"))) %>%
  kable(
    booktabs = TRUE,
    longtable = TRUE,
    align = c("l", rep("r", 6)),  # now only 7 cols
    caption = "Out-of-sample forecast results from simulating 45 series with 3 levels",
    col.names = c(" ", rep(c("h=1", "h=1-8", "h=1-16"), 2)),
    escape = FALSE
  ) %>%
  add_header_above(c(" " = 1, "T = 100" = 3, "T = 300" = 3)) %>%
  {
    tbl <- .
    start <- 1
    for (lvl in unique(row_levels)) {
      end <- start + sum(row_levels == lvl) - 1
      tbl <- tbl %>% pack_rows(lvl, start, end)
      start <- end + 1
    }
    tbl
  }

my_kable
```

```{=latex}
{\footnotesize
\begin{center}
  \textbf{NOTES:} Base shows the average MSE of the base forecasts. A negative (positive) entry above this row shows a percentage decrease (increase) in average MSE relative to the base forecasts.
\end{center}
}
```
